UGAN: Improving Underwater Image Quality using Generative Adversarial Networks

### 2017-09-15 files/paper/paper.tex
Fixed bib entries that were erroneous, and edited some of the related work section. Also fixed missing image references.

\title{UGAN: Underwater Image Restoration using Generative Adversarial Networks}
\author{Cameron Fabbri$^{1}$, Md Jahidul Islam$^{2}$, and Junaed Sattar$^{3}$
\thanks{				
  The authors are with the Department of Computer Science and Engineering, University of Minnesota-Twin  Cities, MN 55455, USA. \newline
 {\tt\small\{$^{1}$fabbr013, $^{2}$islam034, $^{3}$junaed\}@umn.edu}
}
}

@@

\section{Introduction}
%TODO - talk about having to go back to the same location if you want to get good/bad pairs of the ``same'' image.\starnote{I assume Cam will
%do this?}
Underwater robotics has been a steadily growing subfield of autonomous field robotics, assisted by the advent of novel platforms,
sensors and propulsion mechanisms. While autonomous underwater vehicles are often equipped with a variety of sensors, visual sensing is an
attractive option because of its non-intrusive, passive, and energy efficient nature. The monitoring of coral reefs \cite{shkurti2012multi},
deep ocean exploration \cite{whitcomb2000advances}, and mapping of the seabed\starnote{Citation?} are a number of tasks where
visually-guided AUVs and ROVs (Remotely Operated Vehicles) have seen widespread use. Use of these robots ensures humans are not exposed to
the hazards of underwater exploration, as they no longer need to venture to the depths (which was how such tasks were carried out in the
past). Despite the advantages of using vision, underwater environments pose unique challenges to visual sensing, as phenomena such as light
refraction, absorption and scattering from suspended particles can greatly affect the optics of light. As an example, because red
wavelengths are quickly absorbed by water, images tend to have a green or blue hue to them. As one goes deeper, this effect worsens, as more
and more red hue is absorbed. This distortion is extremely non-linear in nature, and is affected by a large number of factors, such as the
amount of light present (overcast versus sunny, operational depth), amount of particles in the water, time of day, and the camera being
used. This may cause difficulty in tasks such as segmentation, tracking, or classification due to their indirect or direct use of color.

@@

\end{tabular}
\label{fig:samples}
\caption{Sample underwater images displaying the diversity of distortion that can occur. Due to the variety of distances
of objects in the image, there is a varying amount of color loss and distortion.}
\end{figure}

@@

While there have been many very successful recent approaches towards automatic colorization
\cite{zhang2016colorful,iizuka2016let}, most are focused on the task of grayscale to color.
The work of \cite{torres2005color} uses an energy minimization formulation using a Markov Random Field. 
Many employ the use of a physics based model to directly model light refraction \cite{jordt2014underwater}.
Most similar to our line of work is the recently proposed WaterGAN \cite{li2017watergan}, which uses an adversarial
approach towards generating realistic underwater images. Their generator model can be broken down into three stages:
1) Attenuation, which accounts for range-dependent attenuation of light.
2) Scattering, which models the haze effect caused by photons scattering back towards the image sensor. 3)
Vingetting, which produces a shading effect on the image corners that can be caused by certain camera lenses.
Opposed to our work, they use a GAN for generating the underwater images and strictly Euclidean loss for color
correction, where as we use a GAN for both. Furthermore, they require depth information during the training of WaterGAN,
whereas we only require two separate image domains throughout.

Recent work in generative models, specifically GANs, have shown great success
in areas such as inpainting \cite{pathak2016context}, style transfer \cite{Gatys_2016_CVPR}, and image-to-image
translation \cite{isola2016image,zhu2017unpaired}. This is highly due to their ability to provide a more meaningful
loss than simply the Euclidean distance, which has been shown to produce blurry results. In our work, we structure
the problem as paired image-to-image translation, using Generative Adversarial Networks (GANs) as our generative model.
Much like the work of \cite{isola2016image}, we use image pairs from two domains an input and ground truth.
\starnote{Somewhere I think we should mention that unpaired image to image translation is more difficult, and
that cyclegan is a good way to generate a dataset in such a way to do this with image pairs.}

@@

\noindent In our experiments, we denote our network as UGAN-P when considering the GDL, which can be expressed as
\starnote{I don't like the - in this equation, but don't know how to change it to be shorter}

\begin{equation}
   \begin{aligned}
      \mathcal{L}_{UGAN-P}^* = \min\limits_{G}\max\limits_{D} \mathcal{L}_{WGAN}(G,D) + & \\
      \lambda_{1} \mathcal{L}_{L1}(G) + & \lambda_{2} \mathcal{L}_{GDL}
   \end{aligned}
\end{equation}

@@

\section{Experiments}
\subsection{Datasets}
We used several subsets of Imagenet \cite{deng2009imagenet} for training and evaluation of our methods. We also
evaluate a tracking algorithm on a diving video taken from Youtube
\footnote{https://www.youtube.com/watch?v=QmRFmhILd5o}. Subsets of Imagenet containing underwater images
were selected for the training of CycleGAN, and manually separated into two classes based on visual inspection. We let
$X$ be the set of
underwater images with no distortion, and $Y$ be the set of underwater images with distortion. $X$ contained 6143
images, and $Y$ contained 1817 images. We then trained CycleGAN to learn the mapping $F: X \rightarrow Y$, such that
images from $X$ appeared to have come from $Y$. Finally, our image pairs for training data were generated by distorting
all images in $X$ with $F$. Figure ~\ref{cgan_samples} shows sample training pairs. When comparing with CycleGAN, we used a test set
of 56 images acquired from Flickr \textsuperscript{TM}.

\subsection{Evaluation}
We train UGAN and UGAN-P on the image pairs generated by CycleGAN, and evaluate on the images from the
test set, $Y$. Note that these images do not contain any ground truth, as they are original distorted images from
Imagenet. Images for training and testing are of size $256 \times 256 \times 3$ and normalized between $[-1, 1]$.
Figure ~\ref{test_samples} shows samples from the test set. Notably, these images contain varying amounts of noise. Both UGAN and UGAN-P
are able to recover lost color information, as well as correct any color information this is present.

While many of the distorted images contain a blue or green hue over the entire image space, that is not always the case.
In certain environments,
it is possible that objects close to the camera are undistorted with correct colors, while the background
of the image contains distortion. In these cases, we would like the network to only correct parts of the image that
appear distorted. The last row in Figure ~\ref{test_samples} shows a sample of such an image. The orange of the clownfish is left
unchanged while the distorted sea anemone in the background has its color corrected.

@@

\subsection{Comparison to CycleGAN}
It is important to note that during the process of learning a mapping $F: X \rightarrow Y$, CycleGAN also learns a
mapping $G: Y \rightarrow X$. Here we show that UGAN and UGAN-P provide superior performance. We use the Canny edge
detector \cite{canny1986computational} to provide a color agnostic evaluation of the images, as the original contain
distorted colors and cannot be compared back to as ground truth. Due to the fact that restoring color information
should not alter the overall structure of the image, we measure the distance in the image space between the edges
found in the original and generated images. Figure ~\ref{canny_samples} shows the original images and results from
edge detection. Table 1 provides the measurements from Figure ~\ref{canny_samples}, as well as the average over the
entire dataset.

We explore the artifacts of content loss, as seen in Figure ~\ref{zoom}. In particular, we compare local statistics
of the highlighted image patches, where each image patch is resized to $64 \times 64$. We use the GDL
\cite{mathieu2015deep} from (\ref{gdl_eq}) as a sharpness measure.

>>>>

\title{UGAN: Improving Underwater Image Quality using Generative Adversarial Networks}
\author{Cameron Fabbri$^{1}$, Md Jahidul Islam$^{2}$, and Junaed Sattar$^{3}$
\thanks{				
  The authors are with the Department of Computer Science and Engineering, University of Minnesota-Twin  Cities, MN 55455, USA. \newline
 {\tt\small\{$^{1}$fabbr013, $^{2}$islam034, $^{3}$junaed\}@umn.edu}
}
}

@@

\section{Introduction}
%TODO - talk about having to go back to the same location if you want to get good/bad pairs of the ``same'' image.\starnote{I assume Cam will
%do this?}
Underwater robotics has been a steadily growing subfield of autonomous field robotics, assisted by the advent of novel platforms,
sensors and propulsion mechanisms. While autonomous underwater vehicles are often equipped with a variety of sensors, visual sensing is an
attractive option because of its non-intrusive, passive, and energy efficient nature. The monitoring of coral reefs \cite{shkurti2012multi},
deep ocean exploration \cite{whitcomb2000advances}, and mapping of the seabed~\cite{bingham2010robotic} are a number of tasks where
visually-guided AUVs and ROVs (Remotely Operated Vehicles) have seen widespread use. Use of these robots ensures humans are not exposed to
the hazards of underwater exploration, as they no longer need to venture to the depths (which was how such tasks were carried out in the
past). Despite the advantages of using vision, underwater environments pose unique challenges to visual sensing, as phenomena such as light
refraction, absorption and scattering from suspended particles can greatly affect the optics of light. As an example, because red
wavelengths are quickly absorbed by water, images tend to have a green or blue hue to them. As one goes deeper, this effect worsens, as more
and more red hue is absorbed. This distortion is extremely non-linear in nature, and is affected by a large number of factors, such as the
amount of light present (overcast versus sunny, operational depth), amount of particles in the water, time of day, and the camera being
used. This may cause difficulty in tasks such as segmentation, tracking, or classification due to their indirect or direct use of color.

@@

\end{tabular}
\label{fig:samples}
\caption{Sample underwater images with natural and man-made artifacts (which in this case is our underwater robot) displaying the 
diversity of distortion that can occur. With the varying camera-to-object distances in the images, the distortion and loss of 
color varies between the different images.}
\end{figure}

@@

While there have been a number of successful recent approaches towards automatic colorization 
\cite{zhang2016colorful,iizuka2016let}, most are focused on the task of converting grayscale images to color. Quite a few 
approaches use a physics-based technique to directly model light refraction~\cite{jordt2014underwater}. Specifically for
restoring color in underwater images, the work of~\cite{torres2005color} uses an energy minimization formulation using a Markov 
Random Field. Most similar to the work proposed in this paper is the recently proposed WaterGAN~\cite{li2017watergan}, 
which uses an adversarial approach towards generating realistic underwater images. Their generator model can be broken down into 
three stages: 1) Attenuation, which accounts for range-dependent attenuation of light. 2) Scattering, which models the haze 
effect caused by photons scattering back towards the image sensor and 3) Vignetting, which produces a shading effect on the 
image corners that can be caused by certain camera lenses. Differentiating from our work, they use a GAN for generating the 
underwater images and use strictly Euclidean loss for color correction, whereas we use a GAN for both. Furthermore, they require 
depth information during the training of WaterGAN, which can be often difficult to attain particularly for underwater 
autonomous robotic applications. Our work only requires images of objects in two separate domains (\emph{e.g.}, underwater 
and terrestrial) throughout the entire process.

Recent work in generative models, specifically GANs, have shown great success in areas such as inpainting 
\cite{pathak2016context}, style transfer \cite{Gatys_2016_CVPR}, and image-to-image translation 
\cite{isola2016image,zhu2017unpaired}. This is primarily due to their ability to provide a more meaningful loss than simply the 
Euclidean distance, which has been shown to produce blurry results. In our work, we structure the problem of estimating 
the true appearance of underwater imagery as a paired image-to-image translation problem, using Generative Adversarial Networks 
(GANs) as our generative model\starnote{this needs a little bit more expansion}. Much like the work of \cite{isola2016image}, we 
use image pairs from two domains as input and ground truth. \starnote{Somewhere I think we should mention that unpaired image to 
image translation is more difficult, and that cyclegan is a good way to generate a dataset in such a way to do this with image 
pairs.}

@@

\noindent In our experiments, we denote our network as UGAN-P when considering the GDL, which can be expressed as
\starnote{JS: DONE. I don't like the - in this equation, but don't know how to change it to be shorter}

\begin{equation}
   \begin{aligned}
      \mathcal{L}_{UGAN\scalebox{0.4}[1.0]{\( - \)}P}^* = \min\limits_{G}\max\limits_{D} \mathcal{L}_{WGAN}(G,D) + & \\
      % \mathcal{L}_{UGAN-P}^* = \min\limits_{G}\max\limits_{D} \mathcal{L}_{WGAN}(G,D) + & \\
      \lambda_{1} \mathcal{L}_{L1}(G) + & \lambda_{2} \mathcal{L}_{GDL}
   \end{aligned}
\end{equation}

@@

\section{Experiments}
\subsection{Datasets}
We used several subsets of Imagenet~\cite{deng2009imagenet} for training and evaluation of our methods. We also evaluate a tracking
algorithm on a video of scuba divers taken from Youtube \footnote{https://www.youtube.com/watch?v=QmRFmhILd5o}. Subsets of Imagenet
containing underwater images were selected for the training of CycleGAN, and manually separated into two classes based on visual
inspection. We let $X$ be the set of underwater images with no distortion, and $Y$ be the set of underwater images with distortion. $X$
contained 6143 images, and $Y$ contained 1817 images. We then trained CycleGAN to learn the mapping $F: X \rightarrow Y$, such that images
from $X$ appeared to have come from $Y$. Finally, our image pairs for training data were generated by distorting all images in $X$ with
$F$. Figure~\ref{fig:cgan_samples} shows sample training pairs. When comparing with CycleGAN, we used a test set of 56 images 
acquired from
Flickr\texttrademark .

\subsection{Evaluation}
We train UGAN and UGAN-P on the image pairs generated by CycleGAN, and evaluate on the images from the
test set, $Y$. Note that these images do not contain any ground truth, as they are original distorted images from
Imagenet. Images for training and testing are of size $256 \times 256 \times 3$ and normalized between $[-1, 1]$.
Figure ~\ref{fig:test_samples} shows samples from the test set. Notably, these images contain varying amounts of noise. Both UGAN 
and UGAN-P
are able to recover lost color information, as well as correct any color information this is present.

While many of the distorted images contain a blue or green hue over the entire image space, that is not always the case.
In certain environments,
it is possible that objects close to the camera are undistorted with correct colors, while the background
of the image contains distortion. In these cases, we would like the network to only correct parts of the image that
appear distorted. The last row in Figure ~\ref{fig:test_samples} shows a sample of such an image. The orange of the clownfish is 
left
unchanged while the distorted sea anemone in the background has its color corrected.

@@

\subsection{Comparison to CycleGAN}
It is important to note that during the process of learning a mapping $F: X \rightarrow Y$, CycleGAN also learns a
mapping $G: Y \rightarrow X$. Here we show that UGAN and UGAN-P provide superior performance. We use the Canny edge
detector \cite{canny1986computational} to provide a color agnostic evaluation of the images, as the original contain
distorted colors and cannot be compared back to as ground truth. Due to the fact that restoring color information
should not alter the overall structure of the image, we measure the distance in the image space between the edges
found in the original and generated images. Figure ~\ref{fig:canny_samples} shows the original images and results from
edge detection. Table 1 provides the measurements from Figure ~\ref{fig:canny_samples}, as well as the average over the
entire dataset.

We explore the artifacts of content loss, as seen in Figure ~\ref{fig:zoom}. In particular, we compare local statistics
of the highlighted image patches, where each image patch is resized to $64 \times 64$. We use the GDL
\cite{mathieu2015deep} from (\ref{gdl_eq}) as a sharpness measure.
